For Induction-Induction, Induction is Enough

### 2019-11-12 paper/paper.tex
π₁ and  π₂ rather than p and q in the definition of models

\begin{alignat*}{5}
  & \rlap{(1) Substitution calculus} \\[0.5em]
  & \Con && : \Set \\
  & \Ty  && : \Con\ra\Set \\
  & \Sub  && : \Con\ra\Con\ra\Set \\
  & \Tm  && : (\Gamma:\Con)\ra\Ty\,\Gamma\ra\Set \\
  & \id && : \Sub\,\Gamma\,\Gamma \\
  & \blank\circ\blank && : \Sub\,\Theta\,\Delta\ra\Sub\,\Gamma\,\Theta\ra\Sub\,\Gamma\,\Delta \\
  & \ass && : (\sigma \circ \delta) \circ \nu = \sigma \circ (\delta \circ \nu) \\
  & \idl && : \id\circ\sigma = \sigma \\
  & \idr && : \sigma\circ\id = \sigma \\
  & \blank[\blank] && : \Ty\,\Delta\ra\Sub\,\Gamma\,\Delta\ra\Ty\,\Gamma \\
  & \blank[\blank] && : \Tm\,\Delta\,A\ra(\sigma:\Sub\,\Gamma\,\Delta)\ra\Tm\,\Gamma\,(A[\sigma]) \\
  & [\id] && : A[\id] = A \\
  & [\circ] && : A[\sigma \circ \delta] = A[\sigma][\delta] \\
  & [\id] && : t[\id] = t \\
  & [\circ] && : t[\sigma \circ \delta] = t[\sigma][\delta] \\
  & \boldsymbol{\cdot} && : \Con \\
  & \epsilon && : \Sub\,\Gamma\,\boldsymbol{\cdot} \\
  & {\boldsymbol{\cdot}\eta} && : \{\sigma : \Sub\,\Gamma\,\boldsymbol{\cdot}\} \ra \sigma = \epsilon \\
  & \blank\ext\blank && : (\Gamma:\Con)\ra\Ty\,\Gamma\ra\Con \\
  & \blank,\blank && : (\sigma:\Sub\,\Gamma\,\Delta)\ra\Tm\,\Gamma\,(A[\sigma])\ra\Sub\,\Gamma\,(\Delta\ext A) \\
  & \p && : \Sub\,(\Gamma\ext A)\,\Gamma \\
  & \q && : \Tm\,(\Gamma\ext A)\,(A[\p]) \\
  & {\ext\beta_1} && : \p\circ(\sigma, t) = \sigma \\
  & {\ext\beta_2} && : \q[\sigma, t] = t \\
  & {\ext\eta} && : (\p, \q) = \id \\
  & {,\circ} && : (\sigma, t)\circ\delta = (\sigma\circ\delta, t[\delta]) \\[0.5em]
  & \rlap{(2) Universe} \\[0.5em]
  & \U && : \Ty\,\Gamma \\
  & \El && : \Tm\,\Gamma\,\U\ra\Ty\,\Gamma \\
  & {\U[]} && : \U[\sigma] = \U \\
  & {\El[]} && : (\El\,a)[\sigma] = \El\,(a[\sigma]) \\[0.5em]
  & \rlap{(3) Inductive parameters} \\[0.5em]
  & \Pi && : (a:\Tm\,\Gamma\,\U)\ra\Ty\,(\Gamma\ext\El\,a)\ra\Ty\,\Gamma \\
  & \blank\oldapp\blank && : \Tm\,\Gamma\,(\Pi\,a\,B)\ra (u : \Tm\,\Gamma\,(\El\,a))
  \ra \Tm\,\Gamma\,(\El\,(B[\id,\,u])) \\
  & {\Pi[]} && : (\Pi\,a\,B)[\sigma] = \Pi\,(a[\sigma])\,(B[\sigma^\uparrow]) \\
  & {\oldapp[]} && : (t\oldapp\alpha)[\sigma] = (t[\sigma])\mathop{\oldapp}(\alpha[\sigma]) \\[0.5em]
  & \rlap{(4) Metatheoretic parameters} \\[0.5em]
  & \Pim && : (T:\Set)\ra(T\ra\Ty\,\Gamma)\ra\Ty\,\Gamma \\
  & \blank\appm \blank && : \Tm\,\Gamma\,(\Pim\,T\,B)\ra(\alpha:T) \ra\Tm\,\Gamma\,(B\,\alpha) \\
  & {\Pim[]} && : (\Pim\,T\,B)[\sigma] = \Pim\,T\,(\lambda \alpha.(B\,\alpha)[\sigma]) \\
  & {\appm[]} && : (t\appm\alpha)[\sigma] = (t[\sigma])\mathop{\appm}\alpha \\[0.5em]
\end{alignat*}
\subsection{Notation and abbreviations}

>>>>

\begin{alignat*}{5}
  & \rlap{(1) Substitution calculus} \\[0.5em]
  & \Con && : \Set \\
  & \Ty  && : \Con\ra\Set \\
  & \Sub  && : \Con\ra\Con\ra\Set \\
  & \Tm  && : (\Gamma:\Con)\ra\Ty\,\Gamma\ra\Set \\
  & \id && : \Sub\,\Gamma\,\Gamma \\
  & \blank\circ\blank && : \Sub\,\Theta\,\Delta\ra\Sub\,\Gamma\,\Theta\ra\Sub\,\Gamma\,\Delta \\
  & \ass && : (\sigma \circ \delta) \circ \nu = \sigma \circ (\delta \circ \nu) \\
  & \idl && : \id\circ\sigma = \sigma \\
  & \idr && : \sigma\circ\id = \sigma \\
  & \blank[\blank] && : \Ty\,\Delta\ra\Sub\,\Gamma\,\Delta\ra\Ty\,\Gamma \\
  & \blank[\blank] && : \Tm\,\Delta\,A\ra(\sigma:\Sub\,\Gamma\,\Delta)\ra\Tm\,\Gamma\,(A[\sigma]) \\
  & [\id] && : A[\id] = A \\
  & [\circ] && : A[\sigma \circ \delta] = A[\sigma][\delta] \\
  & [\id] && : t[\id] = t \\
  & [\circ] && : t[\sigma \circ \delta] = t[\sigma][\delta] \\
  & \boldsymbol{\cdot} && : \Con \\
  & \epsilon && : \Sub\,\Gamma\,\boldsymbol{\cdot} \\
  & {\boldsymbol{\cdot}\eta} && : \{\sigma : \Sub\,\Gamma\,\boldsymbol{\cdot}\} \ra \sigma = \epsilon \\
  & \blank\ext\blank && : (\Gamma:\Con)\ra\Ty\,\Gamma\ra\Con \\
  & \blank,\blank && : (\sigma:\Sub\,\Gamma\,\Delta)\ra\Tm\,\Gamma\,(A[\sigma])\ra\Sub\,\Gamma\,(\Delta\ext A) \\
  & \pi_1 && : \Sub\,\Gamma\,(\Delta\ext A)\ra \Sub\,\Gamma\,\Delta \\
  & \pi_2 && : (\sigma : \Sub\,\Gamma\,(\Delta\ext A))\ra \Tm\,\Gamma\,(A[\pi_1 \sigma]) \\
  & {\pi_1\beta} && : \pi_1(\sigma, t) = \sigma \\
  & {\pi_2\beta} && : \pi_2(\sigma, t) = t \\
  & {\pi\eta} && : (\pi_1\,\sigma, \pi_2\,\sigma) = \sigma \\
  & {,\circ} && : (\sigma, t)\circ\delta = (\sigma\circ\delta, t[\delta]) \\[0.5em]
  & \rlap{(2) Universe} \\[0.5em]
  & \U && : \Ty\,\Gamma \\
  & \El && : \Tm\,\Gamma\,\U\ra\Ty\,\Gamma \\
  & {\U[]} && : \U[\sigma] = \U \\
  & {\El[]} && : (\El\,a)[\sigma] = \El\,(a[\sigma]) \\[0.5em]
  & \rlap{(3) Inductive parameters} \\[0.5em]
  & \Pi && : (a:\Tm\,\Gamma\,\U)\ra\Ty\,(\Gamma\ext\El\,a)\ra\Ty\,\Gamma \\
  & \blank\oldapp\blank && : \Tm\,\Gamma\,(\Pi\,a\,B)\ra (u : \Tm\,\Gamma\,(\El\,a))
  \ra \Tm\,\Gamma\,(\El\,(B[\id,\,u])) \\
  & {\Pi[]} && : (\Pi\,a\,B)[\sigma] = \Pi\,(a[\sigma])\,(B[\sigma^\uparrow]) \\
  & {\oldapp[]} && : (t\oldapp\alpha)[\sigma] = (t[\sigma])\mathop{\oldapp}(\alpha[\sigma]) \\[0.5em]
  & \rlap{(4) Metatheoretic parameters} \\[0.5em]
  & \Pim && : (T:\Set)\ra(T\ra\Ty\,\Gamma)\ra\Ty\,\Gamma \\
  & \blank\appm \blank && : \Tm\,\Gamma\,(\Pim\,T\,B)\ra(\alpha:T) \ra\Tm\,\Gamma\,(B\,\alpha) \\
  & {\Pim[]} && : (\Pim\,T\,B)[\sigma] = \Pim\,T\,(\lambda \alpha.(B\,\alpha)[\sigma]) \\
  & {\appm[]} && : (t\appm\alpha)[\sigma] = (t[\sigma])\mathop{\appm}\alpha \\[0.5em]
\end{alignat*}
\subsection{Notation and abbreviations}
